Associations_PFN_Cognition

### 2022-09-13 Step1_TotalCorticalRepresentation/Associations_PFN_Cognition.Rmd
confidence intervals and standardized coefs

@@

>>>>

# standardize all variables for LMER (separately in Discovery and Replication samples)
```{r}
abcd.data.train.harmonized$PFN3<-(abcd.data.train.harmonized$PFN3-mean(abcd.data.train.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN3,na.rm=TRUE)

abcd.data.train.harmonized$PFN15<-(abcd.data.train.harmonized$PFN15-mean(abcd.data.train.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN15,na.rm=TRUE)

abcd.data.train.harmonized$PFN17<-(abcd.data.train.harmonized$PFN17-mean(abcd.data.train.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.train.harmonized$PFN17,na.rm=TRUE)

abcd.data.test.harmonized$PFN3<-(abcd.data.test.harmonized$PFN3-mean(abcd.data.test.harmonized$PFN3,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN3,na.rm=TRUE)

abcd.data.test.harmonized$PFN15<-(abcd.data.test.harmonized$PFN15-mean(abcd.data.test.harmonized$PFN15,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN15,na.rm=TRUE)

abcd.data.test.harmonized$PFN17<-(abcd.data.test.harmonized$PFN17-mean(abcd.data.test.harmonized$PFN17,na.rm=TRUE))/sd(abcd.data.test.harmonized$PFN17,na.rm=TRUE)

abcd.data.train.harmonized$interview_age<-(abcd.data.train.harmonized$interview_age-mean(abcd.data.train.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.train.harmonized$interview_age,na.rm=TRUE)

abcd.data.test.harmonized$interview_age<-(abcd.data.test.harmonized$interview_age-mean(abcd.data.test.harmonized$interview_age,na.rm=TRUE))/sd(abcd.data.test.harmonized$interview_age,na.rm=TRUE)

abcd.data.train.harmonized$meanFD<-(abcd.data.train.harmonized$meanFD-mean(abcd.data.train.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.train.harmonized$meanFD,na.rm=TRUE)

abcd.data.test.harmonized$meanFD<-(abcd.data.test.harmonized$meanFD-mean(abcd.data.test.harmonized$meanFD,na.rm=TRUE))/sd(abcd.data.test.harmonized$meanFD,na.rm=TRUE)

@@

# get confidence intervals
```{r}
confint(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
confint(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))
confint(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.train.harmonized))

confint(lmer(PFN3~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
confint(lmer(PFN15~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
confint(lmer(PFN17~interview_age+sex+(1|rel_family_id)+meanFD+thompson_PC1,data=abcd.data.test.harmonized))
```
